Manuscript

### 2018-11-21 manuscript.Rmd

  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res),
                          t_statistic = c(round(ccle_lin_p_ttest$statistic, 3), round(ctrp_lin_p_ttest$statistic, 3), round(gdsc_lin_p_ttest$statistic, 3)),
                          df = c(round(ccle_lin_p_ttest$parameter, 3), round(ctrp_lin_p_ttest$parameter, 3), round(gdsc_lin_p_ttest$parameter, 3)),
                          p_value = c(round(ccle_lin_p_ttest$p.value, 3), round(ctrp_lin_p_ttest$p.value, 3), round(gdsc_lin_p_ttest$p.value, 3)),
                          group_general_lineage_name = lineage_name)
  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    geom_text_repel(data = subset(use_data, InG2P == "Yes"), mapping = aes(x = p, y = n, label = Drug_Gene), size = 3, segment.size = 0.2, segment.color = "grey50") +
    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
    labs(x = "Drug-gene association p-value between mutation groups", y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(ylim = c(0, 1)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    coord_flip() +
    labs(x = "In G2P?", title = toupper(lineage_name)) +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
  saveWidgetFix(widget = plot, file = paste0("./plots/manuscript/plotlys_mut_by_lineage/", lineage_name, "_mut_plotly.html"))

@@

```{r}
ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes.rds")
ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
ccle_data_ptmuts$Dataset <- "CCLE"
ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds")
ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
ctrp_data_ptmuts$Dataset <- "CTRP"
ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds")
gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
gdsc_data_ptmuts$Dataset <- "GDSC"
gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
# Filter drug screen datasets for G2P drug-gene associations
ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
# Filter drug screen datasets for G2P drugs and genes
ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
```

@@

```{r fig.height=7, fig.width=12}
crispr_data_signif_g2p_gene_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_g2p_20gene)
crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_gene, by = "Hugo_Symbol")
crispr_data_signif_g2p_gene$Hugo_Symbol <- ordered(crispr_data_signif_g2p_gene$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
crispr_data_signif_g2p_gene_color <- as.character(crispr_data_signif_g2p_gene$Color_Nonsilent)
names(crispr_data_signif_g2p_gene_color) <- crispr_data_signif_g2p_gene$Mutation_Status_Nonsilent
crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene, crispr_data_signif_g2p_gene %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
crispr_data_signif_g2p_gene_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_gene$p.signif, p.signif.adj = crispr_data_signif_g2p_gene$p.signif.adj,  Hugo_Symbol = crispr_data_signif_g2p_gene$Hugo_Symbol, Text_y = crispr_data_signif_g2p_gene$Text_y))
crispr_data_signif_g2p_gene_plot <- ggplot(data = crispr_data_signif_g2p_gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2, scales = "free_y") +
  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = crispr_data_signif_g2p_gene_color) + 
  geom_text(data = crispr_data_signif_g2p_gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif), nudge_y = 0.2) +
  theme(legend.position = "top", axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.x = element_blank()) +
  labs(y = "CERES Score",
       color = "Mutation Status",
       title = "CERES scores for select Level A G2P genes",
       subtitle = "Genes are sorted by increasing p-value.")
crispr_data_signif_g2p_gene_plot
# ggsave("./plots/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
```

@@

```{r fig.height=15, fig.width=15}
crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
crispr_data_signif_g2p_lineage_color <- as.character(crispr_data_signif_g2p_lineage$Color_Nonsilent)
names(crispr_data_signif_g2p_lineage_color) <- crispr_data_signif_g2p_lineage$Mutation_Status_Nonsilent
crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_lineage, crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
crispr_data_signif_g2p_lineage_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_lineage$p.signif, p.signif.adj = crispr_data_signif_g2p_lineage$p.signif.adj,  group_general_lineage_name = crispr_data_signif_g2p_lineage$group_general_lineage_name, Hugo_Symbol = crispr_data_signif_g2p_lineage$Hugo_Symbol, Text_y = crispr_data_signif_g2p_lineage$Text_y))
crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = crispr_data_signif_g2p_lineage_color) +
  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1) +
  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES score by cell line lineage for significant Level A G2P genes",
       subtitle = "* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
crispr_data_signif_g2p_lineage_plot
# ggsave("./plots/manuscript/crispr_crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
```

@@

```{r}
g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
range(g2p_druggene_p_tally$n)
mean(g2p_druggene_p_tally$n)
sd(g2p_druggene_p_tally$n)
g2p_drug_tally <- g2p %>% group_by(Drug) %>% tally() %>% drop_na()
range(g2p_drug_tally$n)
mean(g2p_drug_tally$n)
sd(g2p_drug_tally$n)
g2p_gene_tally <- g2p %>% group_by(Gene) %>% tally() %>% drop_na()
range(g2p_gene_tally$n)
mean(g2p_gene_tally$n)
sd(g2p_gene_tally$n)
```

@@

```{r}
ccle_druggene_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ccle_druggene_summ$n <- ifelse(is.na(ccle_druggene_summ$n), 0, ccle_druggene_summ$n)
ccle_druggene_summ$InG2P <- ifelse(ccle_druggene_summ$n != 0, "Yes", "No")
ccle_druggene_summ$Dataset <- "CCLE"
ccle_p_ttest <- t.test(ccle_druggene_summ$p ~ ccle_druggene_summ$InG2P)
ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 1), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 3))
ctrp_druggene_summ <- merge(g2p_druggene_p_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ctrp_druggene_summ$n <- ifelse(is.na(ctrp_druggene_summ$n), 0, ctrp_druggene_summ$n)
ctrp_druggene_summ$InG2P <- ifelse(ctrp_druggene_summ$n != 0, "Yes", "No")
ctrp_druggene_summ$Dataset <- "CTRP"
ctrp_p_ttest <- t.test(ctrp_druggene_summ$p ~ ctrp_druggene_summ$InG2P)
ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 1), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", round(ctrp_p_ttest$p.value, 3))
gdsc_druggene_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
gdsc_druggene_summ$Dataset <- "GDSC"
gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 1), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", round(gdsc_p_ttest$p.value, 3))
g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res))
g2p_druggene_all_summ$Drug_Gene_Ordered <- factor(g2p_druggene_all_summ$Drug_Gene, levels = as.character(unique(g2p_druggene_all_summ$Drug_Gene)), labels = sapply(strsplit(x = as.character(unique(g2p_druggene_all_summ$Drug_Gene)), split = "_"), function(x) paste0(x[1], "\n", x[2])))
```

>>>>

  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res),
                          t_statistic = c(round(ccle_lin_p_ttest$statistic, 3), round(ctrp_lin_p_ttest$statistic, 3), round(gdsc_lin_p_ttest$statistic, 3)),
                          df = c(round(ccle_lin_p_ttest$parameter, 3), round(ctrp_lin_p_ttest$parameter, 3), round(gdsc_lin_p_ttest$parameter, 3)),
                          p_value = c(round(ccle_lin_p_ttest$p.value, 3), round(ctrp_lin_p_ttest$p.value, 3), round(gdsc_lin_p_ttest$p.value, 3)),
                          group_general_lineage_name = lineage_name)
  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    geom_text_repel(data = subset(use_data, InG2P == "Yes"), mapping = aes(x = p, y = n, label = Drug_Gene), size = 3, segment.size = 0.2, segment.color = "grey50") +
    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
    labs(x = "Drug-gene association p-value between mutation groups", y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(ylim = c(0, 1)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    coord_flip() +
    labs(x = "In G2P?", title = toupper(lineage_name)) +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

  saveWidgetFix(widget = plot, file = paste0("./plots/manuscript/plotlys_mut_by_lineage/", lineage_name, "_mut_plotly.html"))

@@

```{r}
ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes.rds")
ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
ccle_data_ptmuts$Dataset <- "CCLE"
ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds")
ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
ctrp_data_ptmuts$Dataset <- "CTRP"
ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds")
gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
gdsc_data_ptmuts$Dataset <- "GDSC"
gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
# Filter drug screen datasets for G2P drug-gene associations
ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))

# Filter drug screen datasets for G2P drugs and genes
ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
```

@@

```{r fig.height=7, fig.width=12}
crispr_data_signif_g2p_gene_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_g2p_20gene)
crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_gene, by = "Hugo_Symbol")
crispr_data_signif_g2p_gene$Hugo_Symbol <- ordered(crispr_data_signif_g2p_gene$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
crispr_data_signif_g2p_gene_color <- as.character(crispr_data_signif_g2p_gene$Color_Nonsilent)
names(crispr_data_signif_g2p_gene_color) <- crispr_data_signif_g2p_gene$Mutation_Status_Nonsilent
crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene, crispr_data_signif_g2p_gene %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
crispr_data_signif_g2p_gene_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_gene$p.signif, p.signif.adj = crispr_data_signif_g2p_gene$p.signif.adj,  Hugo_Symbol = crispr_data_signif_g2p_gene$Hugo_Symbol, Text_y = crispr_data_signif_g2p_gene$Text_y))
crispr_data_signif_g2p_gene_plot <- ggplot(data = crispr_data_signif_g2p_gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2, scales = "free_y") +
  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = crispr_data_signif_g2p_gene_color) + 
  geom_text(data = crispr_data_signif_g2p_gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif), nudge_y = 0.2) +
  theme(legend.position = "top", axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.x = element_blank()) +
  labs(y = "CERES Score",
       color = "Mutation Status",
       title = "CERES scores for select Level A G2P genes",
       subtitle = "Genes are sorted by increasing p-value.")
crispr_data_signif_g2p_gene_plot

# ggsave("./plots/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
```

@@

```{r fig.height=15, fig.width=15}
crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
crispr_data_signif_g2p_lineage_color <- as.character(crispr_data_signif_g2p_lineage$Color_Nonsilent)
names(crispr_data_signif_g2p_lineage_color) <- crispr_data_signif_g2p_lineage$Mutation_Status_Nonsilent
crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_lineage, crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
crispr_data_signif_g2p_lineage_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_lineage$p.signif, p.signif.adj = crispr_data_signif_g2p_lineage$p.signif.adj,  group_general_lineage_name = crispr_data_signif_g2p_lineage$group_general_lineage_name, Hugo_Symbol = crispr_data_signif_g2p_lineage$Hugo_Symbol, Text_y = crispr_data_signif_g2p_lineage$Text_y))
crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = crispr_data_signif_g2p_lineage_color) +
  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1) +
  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES score by cell line lineage for significant Level A G2P genes",
       subtitle = "* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
crispr_data_signif_g2p_lineage_plot

# ggsave("./plots/manuscript/crispr_crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
```

@@

```{r}
g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
range(g2p_druggene_p_tally$n)
mean(g2p_druggene_p_tally$n)
sd(g2p_druggene_p_tally$n)

g2p_drug_tally <- g2p %>% group_by(Drug) %>% tally() %>% drop_na()
range(g2p_drug_tally$n)
mean(g2p_drug_tally$n)
sd(g2p_drug_tally$n)

g2p_gene_tally <- g2p %>% group_by(Gene) %>% tally() %>% drop_na()
range(g2p_gene_tally$n)
mean(g2p_gene_tally$n)
sd(g2p_gene_tally$n)
```

@@

```{r}
ccle_druggene_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ccle_druggene_summ$n <- ifelse(is.na(ccle_druggene_summ$n), 0, ccle_druggene_summ$n)
ccle_druggene_summ$InG2P <- ifelse(ccle_druggene_summ$n != 0, "Yes", "No")
ccle_druggene_summ$Dataset <- "CCLE"
ccle_p_ttest <- t.test(ccle_druggene_summ$p ~ ccle_druggene_summ$InG2P)
ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 1), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 3))

ctrp_druggene_summ <- merge(g2p_druggene_p_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ctrp_druggene_summ$n <- ifelse(is.na(ctrp_druggene_summ$n), 0, ctrp_druggene_summ$n)
ctrp_druggene_summ$InG2P <- ifelse(ctrp_druggene_summ$n != 0, "Yes", "No")
ctrp_druggene_summ$Dataset <- "CTRP"
ctrp_p_ttest <- t.test(ctrp_druggene_summ$p ~ ctrp_druggene_summ$InG2P)
ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 1), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", round(ctrp_p_ttest$p.value, 3))

gdsc_druggene_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
gdsc_druggene_summ$Dataset <- "GDSC"
gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 1), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", round(gdsc_p_ttest$p.value, 3))

g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res))
g2p_druggene_all_summ$Drug_Gene_Ordered <- factor(g2p_druggene_all_summ$Drug_Gene, levels = as.character(unique(g2p_druggene_all_summ$Drug_Gene)), labels = sapply(strsplit(x = as.character(unique(g2p_druggene_all_summ$Drug_Gene)), split = "_"), function(x) paste0(x[1], "\n", x[2])))
```
